Combining living and fossil taxa into phylogenies: the missing data issue

### 2014-12-18 Manuscript/SupplementaryMaterial/Supp_results.tex
Figures update

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{SupplementaryMaterial/Supp_Figures/TEM_Fig-Appendix-Global-Bootstrap+Treeset-RF+Tr-small.pdf}
\caption{Trend of the effect of missing data on topological recovery on the Bootstraps and the Bayesian posterior trees distributions. The amount of missing data per parameter ($M_{L}$, $M_{F}$ and $M_{C}$) is represented along the x axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data. The topological recovery is represented on the y axis, both using Robinson-Foulds distance (upper row) and Triplets distance (lower row). Points represent the modal value of each distribution ; thick solid and thin dashed lines represents respectively the 50\% and 95\% confidence intervals or the distributions. The Bootstraps are represented in black and the Bayesian posterior trees distributions in grey.}
\label{Fig_global_BootTreesets} %Differences between all the parameters and between two methods (Boot vs treesets)
\end{figure}

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{SupplementaryMaterial/Supp_Figures/TEM_Fig-Appendix-PairComp_permeth.pdf}
\caption{Distribution of the Pairwise Bhattacharyya Coefficients within each method. A- Distribution of the coefficients when comparing Ronbinson-Foulds distances. B- Distribution of the coefficients when comparing Triplets distances.}
\label{Fig_Bhatt.coeff_distribution} %Differences in overlap within each method
\end{figure}

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{SupplementaryMaterial/Supp_Figures/TEM_Fig-Appendix-PairComp_within-Baytre-RF.pdf}
\caption{Pairwise Bhattacharyya Coefficients within the Bayesian posterior trees distributions. The pairwise trees comparisons are represent on both axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data. The matrix represents the values of pairwise Bhattacharyya Coefficients going from green (BC=1) to red (BC=0). Results are calculated for the Normalised Robinson-Foulds distance.}
\label{Fig_pairComp-Baytree-RF}
\end{figure} %Pairwise BC for the Bayesian treesets for RF. (parameters differences)

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{SupplementaryMaterial/Supp_Figures/TEM_Fig-Appendix-PairComp_within-Baytre-Tr.pdf}
\caption{Pairwise Bhattacharyya Coefficients within the Bayesian posterior trees distributions. The pairwise trees comparisons are represent on both axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data. The matrix represents the values of pairwise Bhattacharyya Coefficients going from green (BC=1) to red (BC=0). Results are calculated for the Normalised Triplets distance.}
\label{Fig_pairComp-Baytree-Tr}
\end{figure} %Pairwise BC for the Bayesian treesets for Tr. (parameters differences)

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{SupplementaryMaterial/Supp_Figures/TEM_Fig-Appendix-PairComp_within-MLbest-RF.pdf}
\caption{Pairwise Bhattacharyya Coefficients within the Maximum Likelihood trees. The pairwise trees comparisons are represent on both axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data. The matrix represents the values of pairwise Bhattacharyya Coefficients going from green (BC=1) to red (BC=0). Results are calculated for the Normalised Robinson-Foulds distance.}
\label{Fig_pairComp-MLbest-RF}
\end{figure} %Pairwise BC for the ML for RF. (parameters differences)

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{SupplementaryMaterial/Supp_Figures/TEM_Fig-Appendix-PairComp_within-MLbest-Tr.pdf}
\caption{Pairwise Bhattacharyya Coefficients within the Maximum Likelihood trees. The pairwise trees comparisons are represent on both axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data. The matrix represents the values of pairwise Bhattacharyya Coefficients going from green (BC=1) to red (BC=0). Results are calculated for the Normalised Triplets distance.}
\label{Fig_pairComp-MLbest-Tr}
\end{figure} %Pairwise BC for the ML for Tr. (parameters differences)

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{SupplementaryMaterial/Supp_Figures/TEM_Fig-Appendix-PairComp_within-MLboot-RF.pdf}
\caption{Pairwise Bhattacharyya Coefficients within the Bootstraps. The pairwise trees comparisons are represent on both axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data. The matrix represents the values of pairwise Bhattacharyya Coefficients going from green (BC=1) to red (BC=0). Results are calculated for the Normalised Robinson-Foulds distance.}
\label{Fig_pairComp-MLboot-RF}
\end{figure} %Pairwise BC for the Bootstraps for RF. (parameters differences)

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{SupplementaryMaterial/Supp_Figures/TEM_Fig-Appendix-PairComp_within-MLboot-Tr.pdf}
\caption{Pairwise Bhattacharyya Coefficients within the Bootstraps. The pairwise trees comparisons are represent on both axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data. The matrix represents the values of pairwise Bhattacharyya Coefficients going from green (BC=1) to red (BC=0). Results are calculated for the Normalised Triplets distance.}
\label{Fig_pairComp-MLboot-Tr}
\end{figure} %Pairwise BC for the Bootstraps for Tr. (parameters differences)

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrr}
  \hline
 & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\ 
  \hline
  Maximum likelihood-RF & 0.06 & 0.26 & 0.39 & 0.40 & 0.49 & 0.94 \\ 
  Maximum likelihood-Tr & 0.27 & 0.45 & 0.58 & 0.63 & 0.83 & 1.00 \\ 
  Bayesian consensus-RF & 0.70 & 0.71 & 0.73 & 0.76 & 0.79 & 0.96 \\ 
  Bayesian consensus-Tr & -0.25 & -0.09 & 0.18 & 0.21 & 0.40 & 0.98 \\ 
  Bootstraps-RF & 0.06 & 0.18 & 0.27 & 0.26 & 0.33 & 0.46 \\ 
  Bootstraps-Tr & 0.24 & 0.32 & 0.36 & 0.38 & 0.46 & 0.60 \\ 
  Bayesian posterior trees-RF & 0.16 & 0.22 & 0.32 & 0.34 & 0.42 & 0.65 \\ 
  Bayesian posterior trees-Tr & 0.24 & 0.36 & 0.40 & 0.50 & 0.68 & 0.98 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{SupplementaryMaterial/Supp_Figures/Boot+Baytre-AllParam-RF+Tr.pdf}
\caption{Trend of the effect of missing data on topological recovery on the Bootstraps and the Bayesian posterior trees distributions. The amount of missing data per parameter ($M_{L}$, $M_{F}$ and $M_{C}$) is represented along the x axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data. The topological recovery is represented on the y axis, both using Robinson-Foulds distance (upper row) and Triplets distance (lower row). Points represent the modal value of each distribution ; thick solid and thin dashed lines represents respectively the 50\% and 95\% confidence intervals or the distributions. The Bootstraps are represented in black and the Bayesian posterior trees distributions in grey.}
\label{Fig_global_BootTreesets} %Differences between all the parameters and between two methods (Boot vs treesets)
\end{figure}

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{SupplementaryMaterial/Supp_Figures/BC-AllMethods-RF+Tr.pdf}
\caption{Distribution of the Pairwise Bhattacharyya Coefficients within each method. A- Distribution of the coefficients when comparing Ronbinson-Foulds distances. B- Distribution of the coefficients when comparing Triplets distances.}
\label{Fig_Bhatt.coeff_distribution} %Differences in overlap within each method
\end{figure}

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{SupplementaryMaterial/Supp_Figures/PairwiseComp-ML-RF+Tr.pdf}
\caption{Pairwise Bhattacharyya Coefficients within the Maximum Likelihood trees. The pairwise trees comparisons are represent on both axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data for each parameter. The matrix represents the values of pairwise Bhattacharyya Coefficients going from green (1) to red (0). A. Results for the Normalised Robinson-Foulds distance. B. Results with the for Normalised Triplets distance.}
\label{Fig_pairComp-Baytree-RF}
\end{figure} %Pairwise BC for the ML for RF+Tr. (parameters differences)

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{SupplementaryMaterial/Supp_Figures/PairwiseComp-Boot-RF+Tr.pdf}
\caption{Pairwise Bhattacharyya Coefficients within the Bootstrap trees. The pairwise trees comparisons are represent on both axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data for each parameter. The matrix represents the values of pairwise Bhattacharyya Coefficients going from green (1) to red (0). A. Results for the Normalised Robinson-Foulds distance. B. Results with the for Normalised Triplets distance.}
\label{Fig_pairComp-Baytree-Tr}
\end{figure} %Pairwise BC for the Boot for RF+Tr. (parameters differences)

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{SupplementaryMaterial/Supp_Figures/PairwiseComp-Baytre-RF+Tr.pdf}
\caption{Pairwise Bhattacharyya Coefficients within the Bayesian posterior distribution trees. The pairwise trees comparisons are represent on both axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data for each parameter. The matrix represents the values of pairwise Bhattacharyya Coefficients going from green (1) to red (0). A. Results for the Normalised Robinson-Foulds distance. B. Results with the for Normalised Triplets distance.}
\label{Fig_pairComp-MLbest-RF}
\end{figure} %Pairwise BC for the Baytre for RF+Tr. (parameters differences)

\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrr}
  \hline
 & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\ 
  \hline
  Maximum likelihood-RF & 0.06 & 0.26 & 0.40 & 0.41 & 0.50 & 0.95 \\ 
  Maximumlikelihood-Tr & 0.29 & 0.45 & 0.59 & 0.63 & 0.84 & 1.00 \\ 
  Bayesian consensus-RF & 0.69 & 0.71 & 0.72 & 0.76 & 0.79 & 0.96 \\ 
  Bayesian consensus-Tr & -0.28 & -0.11 & 0.17 & 0.19 & 0.37 & 0.98 \\ 
  Bootstraps-RF & 0.06 & 0.18 & 0.27 & 0.26 & 0.34 & 0.46 \\ 
  Bootstraps-Tr & 0.23 & 0.31 & 0.35 & 0.38 & 0.45 & 0.58 \\ 
  Bayesian posterior trees-RF & 0.16 & 0.22 & 0.32 & 0.34 & 0.42 & 0.65 \\ 
  Bayesian posterior trees-Tr & 0.24 & 0.35 & 0.40 & 0.50 & 0.67 & 0.98 \\ 
   \hline
   \hline
\end{tabular}
\end{table}

### 2014-12-18 Manuscript/TEM_draft.tex
Figures update

\begin{figure}
\centering
    \includegraphics[keepaspectratio=true]{Figures/BW/TEM_Fig_outline-BW.pdf}
\caption{Protocol outline.
(1) We randomly generated a birth-death tree (the "true" tree) and used it to infer a matrix with no missing data (the "complete" matrix).
(2) We removed data from the morphological part of the "complete" matrix resulting in 125 "missing-data" matrices.
(3) We built phylogenetic trees from each matrix using both Maximum Likelihood and Bayesian methods.
(4) We compared the "missing-data" trees to the "best" tree.
We repeated the 4 steps 50 times.}
\label{Fig_Outline}
\end{figure}

@@

Next, we generated a molecular and a morphological matrix from the "true" tree. The molecular matrix was inferred from the "true" tree using the R package phyclust v0.1-14 \citep{chen2011}. The matrix contained 1000 character sites for 51 taxa and was generated using the seqgen algorithm \citep{ranbaut1997seqgen} and using the HKY model \citep{HKY85} with random base frequencies and transition/transversion rate of 2 \citep{douadycomparison2003}. The substitution rates were distributed following a gamma distribution with an alpha ($\alpha$) shape of 0.5 \citep{yangamong-site1996}. We chose a low value of $\alpha$ to reduce the number of sites with high substitution rates, thus avoiding too much homoplasy and a decrease in phylogenetic signal. We selected the parameters above to generate data with no special assumption about how the characters evolved, and to reduce the computational time required if these parameters were estimated rather than defined in the tree building part of the analysis (even with the parameters defined, total computational time for the whole analysis was over 150 CPU years). All the molecular information for fossil taxa was replaced by missing data ("?").

@@

On these selected simulations, we used the fast bootstrap algorithm and performed 1000 bootstraps per tree inference to assess the topological support \citep{pattengale2010many}.
%The bootstrap algorithm used in RAxML is the Lazy Sub-tree Rearrangement (LSR) which consists of pruning one sub-tree from the tree and subsequently reinserting it to all neighbouring branches \citep{stamatakisa2008}. Sub-tree Pruning and Reinserting methods (SPR) have been demonstrated to be better than other methods (e.g. Nearest Neighbouring Interchange - NNI) for recovering good bootstrap values \citep{salamin2003}. %TG: The explanations of the algorithm part for the BS was proposed by Trevor I think it's useless
When using these parameters, it took $~$8 CPU years to build 50 sets of 125 bootstrapped Maximum Likelihood trees (8 core nodes 2.30GHz clock speed).

@@

We used these prior to speed up the Bayesian estimation process. These priors biased the way the Bayesian process calculated branch lengths by giving non-random starting points and boundaries for parameter estimation, however, here we are focusing on the effect of missing data on tree topology and not branch lengths. Even using these priors, it took $~$140 CPU years to build 50 sets of 125 Bayesian trees (8 core nodes 2.30GHz clock speed).

@@

\subsection{Comparing topologies}
We compared the topology of the "missing-data" trees to the "best" tree to measure the effect of the three parameters $M_{L}$, $M_{F}$ and $M_{C}$ on tree topology. We used the Robinson-Foulds distance \citep{RF1981} to assess the amount conserved clade positions and the Triplets distance \citep{dobson1975triplets} to assess amount of wildcard taxa \citep{kearneyfragmentary2002}. We then used Normalized Tree Similarity index \citep{Bogdanowicz2012} to generalize our results for any \textit{n} number of taxa. These metrics are described in detail below.
%ADD KHUNAR PAPER SOMEWHERE

@@

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{Figures/colour/Parameters-AllMethods-RF+Tr-small.pdf}
\caption{Comparison between the effect of missing data and the tree inference method on topology. The amount of missing data for each parameter is represented on the x axis. The topology is represented on the y axis, both using Robinson-Foulds distance (upper row) and Triplets distance (lower row). Points represent the modal value of each distribution ; thick solid and thin dashed lines represents respectively the 50\% and 95\% confidence intervals or the distributions. The Maximum Likelihood trees are represented in black, the Bayesian consensus trees in red, the bootstrap trees in green and the posterior tree distribution in blue.}
\label{Fig_Results-permeth_perparam} %Differences within a subset of parameters and between methods
\end{figure}

@@

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{Figures/BW/Global-ML+consensus-RF+Tr-small.pdf}
\caption{Trend of the effect of missing data on topology on the Maximum Likelihood and the Bayesian consensus trees. The amount of missing data per parameter ($M_{L}$, $M_{F}$ and $M_{C}$) is represented along the x axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data for each parameter. The topology is represented on the y axis, both using Robinson-Foulds distance (upper row) and Triplets distance (lower row). Points represent the modal value of each distribution ; thick solid and thin dashed lines represents respectively the 50\% and 95\% confidence intervals or the distributions. The Maximum Likelihood trees are represented in black and the Bayesian consensus trees in grey.}
\label{Fig_Results-global_perparam} %Differences between all the parameters and between two methods (ML vs BC)
\end{figure}

@@

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{Figures/colour/PairComp_without-RF+Tr.pdf}
\caption{Distribution of the Bhattacharyya Coefficients between methods. Curves represents the kernel density estimations of the Bhattacharyya Coefficients between the four different methods. A. Results for the Normalised Robinson-Foulds distance. B. Results with the for Normalised Triplets distance. Pikes around the two different extremes values of the Bhattacharyya Coefficients show the two pairs of most dissimilar methods (Bayesian consensus vs. Bootstraps and Bayesian consensus vs. Bayesian posterior trees) for the Normalised Robinson-Foulds distance ; and the most similar methods (Bootstraps and Bayesian posterior trees) for the Normalised Triples methods.}
\label{Fig_Results-paircomp_without} %Comparisons between methods, both in RF and Triplets.(method differences)
\end{figure}

@@

%Hidden figure for 'fast' build
%\begin{figure} 
%\centering
%    \includegraphics[width=1\textwidth]{Figures/colour/PairComp_within-Baycon-RF+Tr.pdf}
%\caption{Pairwise Bhattacharyya Coefficients within the Bayesian consensus trees. The pairwise trees comparisons are represent on both axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data for each parameter. The matrix represents the values of pairwise Bhattacharyya Coefficients going from green (1) to red (0). A. Results for the Normalised Robinson-Foulds distance. B. Results with the for Normalised Triplets distance.}
\label{Fig_Results-paircomp_within}
%\end{figure} %Pairwise BC for the Bayesian consensus trees for RF and TR. (parameters differences)

@@

%Ignore for 'fast' pdf building
%\section{Supplementary Material}

%    \input{SupplementaryMaterial/SupplementaryMaterial}
%    \label{SupplementaryMaterial}

>>>>

\begin{figure}
\centering
    \includegraphics[keepaspectratio=true]{Figures/In_main/Simulations_outline-BW.pdf}
\caption{Protocol outline.
(1) We randomly generated a birth-death tree (the "true" tree) and used it to infer a matrix with no missing data (the "complete" matrix).
(2) We removed data from the morphological part of the "complete" matrix resulting in 125 "missing-data" matrices.
(3) We built phylogenetic trees from each matrix using both Maximum Likelihood and Bayesian methods.
(4) We compared the "missing-data" trees to the "best" tree.
We repeated the 4 steps 50 times.}
\label{Fig_Outline}
\end{figure}

@@

Next, we generated a molecular and a morphological matrix from the "true" tree. The molecular matrix was inferred from the "true" tree using the R package phyclust v0.1-14 \citep{chen2011}. The matrix contained 1000 character sites for 51 taxa and was generated using the seqgen algorithm \citep{ranbaut1997seqgen} and using the HKY model \citep{HKY85} with random base frequencies and transition/transversion rate of 2 \citep{douadycomparison2003}. The substitution rates were distributed following a gamma distribution with an alpha ($\alpha$) shape of 0.5 \citep{yangamong-site1996}. We chose a low value of $\alpha$ to reduce the number of sites with high substitution rates, thus avoiding too much homoplasy and a decrease in phylogenetic signal. We selected the parameters above to generate data with no special assumption about how the characters evolved, and to reduce the computational time required if these parameters were estimated rather than defined in the tree building part of the analysis (even with the parameters defined, total computational time for the whole analysis was around 150 CPU years). All the molecular information for fossil taxa was replaced by missing data ("?").

@@

On these selected simulations, we used the fast bootstrap algorithm and performed 1000 bootstraps per tree inference to assess the topological support \citep{pattengale2010many}.
%The bootstrap algorithm used in RAxML is the Lazy Sub-tree Rearrangement (LSR) which consists of pruning one sub-tree from the tree and subsequently reinserting it to all neighbouring branches \citep{stamatakisa2008}. Sub-tree Pruning and Reinserting methods (SPR) have been demonstrated to be better than other methods (e.g. Nearest Neighbouring Interchange - NNI) for recovering good bootstrap values \citep{salamin2003}. %TG: The explanations of the algorithm part for the BS was proposed by Trevor I think it's useless
When using these parameters, it took $~$8 CPU years to build 50 sets of 125 bootstrapped Maximum Likelihood trees (2.30GHz clock speed nodes).

@@

We used these prior to speed up the Bayesian estimation process. These priors biased the way the Bayesian process calculated branch lengths by giving non-random starting points and boundaries for parameter estimation, however, here we are focusing on the effect of missing data on tree topology and not branch lengths. Even using these priors, it took $~$140 CPU years to build 50 sets of 125 Bayesian trees (2.30GHz clock speed nodes).

@@

\subsection{Comparing topologies}
We compared the topology of the "missing-data" trees to the "best" tree to measure the effect of the three parameters $M_{L}$, $M_{F}$ and $M_{C}$ on tree topology. We used the Robinson-Foulds distance \citep{RF1981} to assess the amount conserved clade positions and the Triplets distance \citep{dobson1975triplets} to assess amount of wildcard taxa \citep{kearneyfragmentary2002}. We then used Normalized Tree Similarity index \citep{Bogdanowicz2012} to generalize our results for any \textit{n} number of taxa. These metrics are described in detail below.

@@

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{Figures/In_main/AllMethods-RF+Tr-colour.pdf}
\caption{Comparison between the effect of missing data and the tree inference method on topology. The amount of missing data for each parameter is represented on the x axis. The topology is represented on the y axis, both using Robinson-Foulds distance (upper row) and Triplets distance (lower row). Points represent the modal value of each distribution ; thick solid and thin dashed lines represents respectively the 50\% and 95\% confidence intervals or the distributions. The Maximum Likelihood trees are represented in black, the Bayesian consensus trees in red, the bootstrap trees in green and the posterior tree distribution in blue.}
\label{Fig_Results-permeth_perparam} %Differences within a subset of parameters and between methods
\end{figure}

@@

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{Figures/In_main/ML+Baycon-AllParam-RF+Tr-BW.pdf}
\caption{Trend of the effect of missing data on topology on the Maximum Likelihood and the Bayesian consensus trees. The amount of missing data per parameter ($M_{L}$, $M_{F}$ and $M_{C}$) is represented along the x axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data for each parameter. The topology is represented on the y axis, both using Robinson-Foulds distance (upper row) and Triplets distance (lower row). Points represent the modal value of each distribution ; thick solid and thin dashed lines represents respectively the 50\% and 95\% confidence intervals or the distributions. The Maximum Likelihood trees are represented in black and the Bayesian consensus trees in grey.}
\label{Fig_Results-global_perparam} %Differences between all the parameters and between two methods (ML vs BC)
\end{figure}

@@

\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{Figures/In_main/BC-MethodComp-RF+Tr-colour.pdf}
\caption{Distribution of the Bhattacharyya Coefficients between methods. Curves represents the kernel density estimations of the Bhattacharyya Coefficients between the four different methods. A. Results for the Normalised Robinson-Foulds distance. B. Results with the for Normalised Triplets distance. Pikes around the two different extremes values of the Bhattacharyya Coefficients show the two pairs of most dissimilar methods (Bayesian consensus vs. Bootstraps and Bayesian consensus vs. Bayesian posterior trees) for the Normalised Robinson-Foulds distance ; and the most similar methods (Bootstraps and Bayesian posterior trees) for the Normalised Triples methods.}
\label{Fig_Results-paircomp_without} %Comparisons between methods, both in RF and Triplets.(method differences)
\end{figure}

@@

%Hide this figure for 'fast' build
\begin{figure} 
\centering
    \includegraphics[width=1\textwidth]{Figures/In_main/PairwiseComp-Baycon-RF+Tr-colour.pdf}
\caption{Pairwise Bhattacharyya Coefficients within the Bayesian consensus trees. The pairwise trees comparisons are represent on both axis. The colour gradient from white to black represents respectively, 0\%, 10\%, 25\%, 50\% and 75\% of missing data for each parameter. The matrix represents the values of pairwise Bhattacharyya Coefficients going from green (1) to red (0). A. Results for the Normalised Robinson-Foulds distance. B. Results with the for Normalised Triplets distance.}
\label{Fig_Results-paircomp_within}
\end{figure} %Pairwise BC for the Bayesian consensus trees for RF and TR. (parameters differences)

@@

%Ignore this for 'fast' pdf building
\section{Supplementary Material}

    \input{SupplementaryMaterial/SupplementaryMaterial}
    \label{SupplementaryMaterial}
